A quantum parallel Markov chain Monte Carlo

### 2023-01-17 main.tex
small change to caption

 \begin{figure}[!t]
	\centering
	\includegraphics[width=0.9\linewidth]{blackHole.png}
	\caption{On the left is a $4076\times4076$ intensity map of the shadow of supermassive black hole Sagittarius A*  \citep{akiyama2022first}.  On the right is the pixelwise posterior mode of a Bayesian image classification model fit to intensity data.  Within a Metropolis-in-Gibbs routine, quantum parallel MCMC requires less that one-tenth the posterior evaluations required by conventional parallel MCMC.}\label{fig:blackHole}
\end{figure}

>>>>

 \begin{figure}[!t]
	\centering
	\includegraphics[width=0.9\linewidth]{blackHole.png}
	\caption{On the left is a 4,076-by-4,076 intensity map of the shadow of supermassive black hole Sagittarius A*  \citep{akiyama2022first}.  On the right is the pixelwise posterior mode of a Bayesian image classification model fit to intensity data.  Within a Metropolis-in-Gibbs routine, quantum parallel MCMC using 1,024 proposals requires less that one-tenth the posterior evaluations required by conventional parallel MCMC.}\label{fig:blackHole}
\end{figure}
